Paper 2, Econ 980x

### 2022-11-28 Paper2.Rmd
commit

ddi <- read_ipums_ddi("atus_00005.dat")
data <- read_ipums_micro(ddi)

csv <- read_csv(file = "atus_00001.csv.gz") %>%
  clean_names()

@@

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```

>>>>

ddi <- read_ipums_ddi("atus_00005.xml")
csv <- read_ipums_micro(ddi) %>%
  clean_names()

data

#csv <- read_csv(file = "atus_00001.csv.gz") %>%
 # clean_names()

@@

# employed
csv <- csv %>%
  mutate(empstat_cps8 = as.numeric(empstat_cps8)) %>%
  mutate(emp = ifelse(empstat_cps8<= 2, "Employed", ifelse(empstat_cps8>=5, "Not In Labour Force", "Unemployed")))

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```
```{r employment}

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(year) %>%
  count(emp) %>%
  filter(emp == "Unemployed") %>%
  ggplot(mapping = aes(x = year, y = n)) +
  geom_line() 
  #facet_wrap(~emp)

newcsv1 %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram() +
  facet_wrap(~emp)

newcsv1 %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Distribution of annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Distribution of annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)
